Explorations to Optimize the Parareal Algorithm \\to Solve ODEs in Given Applications

### 2014-12-09 paper.tex
more updates

In general, the division in space paradigm is more intuitive to parallelize and will often lead to greater speedups because there is no serial component.  Yet it is worth noting that knowing how to divide the result vector requires knowledge of problem-specific details.  Thus, this approach lacks the generalisability and theoretical derivaions that schemes that parallelize in time can offer.

@@

@@

bksim TODO

@@

We wished to explore certain tests that would span the space of possible
parameters to the parareal as well as possible applications in different ODE
systems. Our baseline was looking to compare

@@

We looked at both $e^x$ as well as TODO WHAT OTHER SCHEME using GET PARAMETERES

@@

For the speaker problem, we designed a problem-specific method to parallelize in space and divide Pierce Hall into subsections such that each processor would receive a division of the building to compute.

bksim TODO

@@

@@

TODO Wesley

>>>>

In general, the division in space paradigm is more intuitive to parallelize and will often lead to greater speedups because there is no serial component.  Yet it is worth noting that knowing how to divide the result vector requires knowledge of problem-specific details.  Thus, this approach lacks the generalizability and theoretical derivaions that schemes that parallelize in time can offer.

@@

The beauty is the parareal method can be adapted into many different versions with different choices of the $g_{\Delta t}$ and $g_{fine}$ solution operators.  The $g_{fine}$ solution is to a more computationally expensive method but assumed to provide either greater resolution or lower error.  Most of the time this will be a higher order method, but can also be a greater sampling of the same order method used in the coarse version.  The exact optimum pairing is problem-specific and the code is written so that a different "n-order method step" function could be written and then replaced into the code.

@@

bksim TODO put a graph because maybe it'll help? the slides have a version

@@

We wished to explore certain tests that would span the space of possible
parameters to the parareal as well as possible applications in different ODE
systems. Because there were so many different versions and parameteres for the parareal to test,

@@

We looked at both $e^x$ as well as TODO WHAT OTHER SCHEME using WHAT WERE THE PARAMETERS - Coarse and Fine Num Steps

@@

For the speaker problem, we designed a problem-specific method to parallelize in space and divide Pierce Hall into subsections such that each processor would receive a division of the building to compute. We wish to strong scaling, in which the computation time of our parallel method will decrease as we increase the number of processors. We compare this version to the serial version we did for Homework 4.

bksim TODO GET DATA, AS REQUIRED FROM ABOVE, SHOW GRAPHS

@@

Now with 3 different parallel implementations, two in time wiht the parareal, one in space,  we compare across take a breather, don't overwork,

@@

TODO WESLEY
